Quantitative Benchmarking for Automatically Generated Conjectures

### 2017-09-07 TEBenchmarkPaper/article.tex
Change titlematter
Add abstract

\title{Quantitative Benchmarking for Theory Exploration%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\author{Chris Warburton% \and
        Alison Pease
        % TODO: Invite Katya? Even if she only offers some help, can acknowledge
}

@@

\institute{C. Warburton \at
              University of Dundee \\
              \email{cmwarburton@dundee.ac.uk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           %\and
           %S. Author \at
           %   second address
}

@@

\begin{abstract}
  % TODO: Write abstract sooner rather than layer
Insert your abstract here. Include keywords, PACS and mathematical
subject classification numbers as needed.
\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

>>>>

\title{Quantitative Benchmarking for Automatically Generated Conjectures%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}
% \subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\author{Chris Warburton \and
        Alison Pease
        % TODO: Invite Katya? Even if she only offers some help, can acknowledge
}

@@

\institute{C. Warburton \at
           University of Dundee \\
           \email{c.m.warburton@dundee.ac.uk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           A. Pease \at
           University of Dundee \\
           \email{a.pease@dundee.ac.uk}
}

@@

\begin{abstract}
  We propose a benchmark suite for evaluating the efficiency and effectiveness
  of automated tools for \emph{theory exploration} or
  \emph{conjecture formation} in higher-order, inductive theories; a domain
  especially suitable for programming language libraries. By providing standard
  tools and metrics, we hope to encourage innovation and comparison between the
  disparate approaches currently being pursued, and spur improvements similar to
  those seen in the competitive field of automated theorem proving.
%\keywords{First keyword \and Second keyword \and More}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}
